TwinPeaks2018

### 2018-05-23 doc/ms.tex
Do standard NS case

\section{Nested Sampling distribution}
Consider the following distribution:
\begin{align}
p_{\rm NS}(x, y) &= \frac{\pi(x, y)}{C X(x, y)}.
\end{align}
Compared to the prior $\pi$, this puts more weight at high values of
$x$ and $y$.

>>>>

\section{Nested Sampling distribution}
Consider the one-scalar situation (i.e., $f(x) \equiv$ log likelihood),
which is the case in standard NS. The Nested Sampling distribution is
\begin{align}
p_{\rm NS}(x) &= \frac{\pi(x)}{C X(x)}.
\end{align}
This is the distribution that `stretches out' the prior (which is a
reflected exponential for $\ln X$) into a uniform distribution for $\ln X$.
\begin{align}
p_{\rm NS}(x) &= \frac{\pi(x)}{C X(x)}.
\end{align}

The KL divergence from $p_{\rm NS}$ to a constrained distribution
$p(x; x^*) = \pi(x)\mathds{1}(x > x^*)/X(x^*)$ is
\begin{align}
D_{\rm KL}\left(p(x; x^*) \,||\, p_{\rm NS}\right)
    &= \int p(x; x^*)
            \log \left[\frac{p_{\rm NS}}{p_{\rm NS}}\right] \, dx \\
    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
    &= \log C + \int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx
\end{align}

Do a change of variables to make $X$ the integrand. Its prior is uniform
because $X$ is a cumulative probability.

\section{Nested Sampling distribution --- TwinPeaks case}

Consider the following distribution:
\begin{align}
p_{\rm NS}(x, y) &= \frac{\pi(x, y)}{C X(x, y)}.
\end{align}
Compared to the prior $\pi$, this puts more weight at high values of
$x$ and $y$.
